quollr: An R Package for Visualizing $2-\\text{D}$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-08 paper-quollr.Rmd
Updated the flow of generating 2D model

## Usage

@@

### Main function

@@

@@

```{r, echo=TRUE}
scurve_umap_scaled <- scurve_nldr_obj$scaled_nldr

lim1 <- scurve_nldr_obj$lim1
lim2 <- scurve_nldr_obj$lim2
r2 <- diff(lim2)/diff(lim1) 
```

We can calculate the `r2`, which represents the ratio of the ranges of the original embedding components.

Constructing the $2\text{-}D$ model primarily involves (i) binning data, (ii) obtaining bin centroids, and (iii) connecting centroids with line segments to indicate neighbors.

>>>>

<!-- ## Usage -->

@@

## Main function

@@

Constructing the $2\text{-}D$ model primarily involves (i) scaling the NLDR data, (ii) binning the data, (iii) obtaining bin centroids, (iv) connecting centroids with line segments to indicate neighbors, and (v) Remove low-density hexagons.

@@
